\documentclass[12pt,a4paper,british,landscape]{article}

\usepackage[fontsize=19.01pt]{fontsize}

\renewcommand*\ttdefault{cmvtt}
\renewcommand{\familydefault}{\ttdefault}

\usepackage[OT2,T1]{fontenc}

\renewcommand\labelitemi{---}


\usepackage{graphicx}
\usepackage[
    a4paper,
    bindingoffset=0cm,
    left=1cm,
    right=1cm,
    top=1.2cm,
    bottom=0cm,
    footskip=0cm
]{geometry}

\frenchspacing              % Better looking spacings after periods
\pagestyle{empty}           % No pagenumbers/headers/footers



\begin{document}




\begin{center}

unlike painting and sculpture, music and theater had arisen within bourgeois culture as diversions, as distractions from quotidian problems--in effect, as escape mechanisms. western music was founded on the principle of suspended resolution, within the calculus of dominant harmony. [\dots]
when long durations appeared in this cultural framework, their dialogical shock was immediately felt; it went directly to the core presuppositions of bourgeois cultural construction. the social reasons for the distraction of the viewer came immediately to the surface: the bourgeois cultural framework had been constructed upon the premise that there was a desperate longing amid the middle class for release from the anxiety-production that mobilized their lives, and that they could be tempted to believe in this resolution only by the suggested assuagement that a dispersal of anxieties into a welter of fantasy identifications with imaginary conflicts and repeated, successive, overlapping and interlocking releases might provide.
this dense tapestry of defenses was stripped away by the minimalist temporal logic of long durations.
instead of the distraction offered by the undulations of conflict and resolution that had inhabited the temporal spaces of western theater and music, audiences were baldly confronted with denied expectations.
conflict and resolution had in effect shrunk the field of durations within western art by centering upon the use of distraction: of repetitive conflict resolution and the momentary use of novelty or variation.
with long durations, the audience found itself immersed in another and quite opposite system of anticipation, one captured in the tidy psychological aperçu that a watched pot never boils. this "never" fully captures the sense in which long durations were not only "long," but that they implemented a sense of duration that was even longer than "long."
duration, that is, was exposed as non-linear, as paradoxical; as capable of overturning the psychic state of bourgeois expectation.

\vspace{0.5cm}

(tony conrad, 2004)

\end{center}

\end{document}

